---
title: "Tiler Vignette"
author: "Christiaan Pauw"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
```

```{r libraries}
library(Tiler)
library(httr)
library(glue)
```

# What this document is about

The document demonstrates the functionality of the Tiler package. 

# Setup

First you have to set up the connection to kubernetes cluster running ComposeDB.

## From a local machine when composedDB was installed with K8S

Look at your namespaces. 

```{r namespaces}
listK8sNamespaces() %>% knitr::kable(format = "pipe")
```

Mine is called `ceramic`.

Get the name of the user

```{r secret}
listK8sSecrets() %>% knitr::kable(format = "pipe")
```

Mine is `ceramic-admin`

```{r constants}
clustername <- "composedb"
namespace <- "ceramic"
```


Get your key with your namespace and name. Default options (field = "data", subfield = "private-key") should work. 

```{r key}
key <- getK8sSecrets(namespace = "ceramic", 
                     name = "ceramic-admin", 
                     field = "data", subfield = "private-key")
```

Get the external URL

```{r externalurl}}
 URL <- getK8sServices()$EXTERNAL_IP
```

Check the status 

```{r status}
res <- httr::GET(glue("http://{URL}:7007/api/v0/node/healthcheck"))
httr::status_code(res)
```

Try to set port forwarding, but it doesn't work. Rather make \texttt{CERAMIC_URL} the remote URL. 


```{r remoteurl}
# system(glue("kubectl port-forward --namespace {namespace} composedb-0 7007:7007"))
REMOTE_URL <- glue::glue("http://{URL}:{7007}")
```

# Tiles

Lets create a tile. 

```{r tile}}
mtcarSID <- glaze_tile_create(CERAMIC_URL = REMOTE_URL, 
                              k = key, 
                              content = jsonlite::toJSON(mtcars[1:2,]))
```

The stream ID is: `r mtcarSID`

We can use this to see the content:

```{r content}
dfContent <- glaze_tile_content(STREAMID = mtcarSID, 
                    CERAMIC_URL = REMOTE_URL, 
                    k = key, 
                    returnJSON = FALSE) 
knitr::kable(dfContent, digits = 1)
```

Lets try to update it with the next to lines of mtcars: 

```{r update}
glaze_tile_update(STREAMID = mtcarSID, 
                  CERAMIC_URL = REMOTE_URL,   
                  k = DID_PRIVATE_KEY, 
                  content = jsonlite::toJSON(mtcars[3:4,]))
```

Now it didn't append, it replaced! We can build our own updater that appends, but this will be expensive with large data sets. 

# Models

The function getComposeDBModelContent is not yet implemented correctly.

```{r modelcontent}
# getComposeDBModelContent(url = "http://146.190.6.248:7007" )
```

